---
title: "About this site"
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
library(riem)
library(httr)
library(sf)
library(gganimate)
library(gifski)
library(png)
library(dplyr)
library(patchwork)
library(ggthemes)
library(distill)
library(knitr)
library(rmarkdown)

h_raw_url <- "https://api.covidactnow.org/v2/states.timeseries.csv?apiKey=a13da1a6818345c697cc89ea4554529a"
h_raw_data <- as_tibble(read_csv(h_raw_url))

```
This website and all it contains is part of my final project in [Kane's free data science bootcamp](https://bootcamp.davidkane.info/). Given the opportunity to explore any data I wanted to, I decided to try and find just how effective vaccinations are in the United States. I did so with two main metrics, the daily vaccination count, and the daily case count. By analyzing the rates of infections in relation to those of vaccinations, I was able to graphically demonstrate that an increase in vaccination counts lead to a decrease in infections rates

## Limitations
One of the largest limitations of this project is the lack of additional information regarding the daily case count. Factors such as lockdowns, the amount of mask usage and different variants would have greatly enhanced my analysis, and would have shown the impact of various preventative measures, not just vaccines. 


## Dataset used to create the graphs 
```{r}
paged_table(h_raw_data)
```
*Please note that this is not the complete table of information, and it only contains the first 10,000 rows of the data set. Because the data is being updated everyday, I highly recommend you check out [Covidactnow](https://apidocs.covidactnow.org/) to download and access the full dataset. In addition you can find explanation of every column and what it means.*
