---
title: "Covid Cases and Vaccination Rates in the US"
description: |
  The relationship between Covid cases and vaccination rates in the US
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(riem)
library(httr)
library(sf)
library(gganimate)
library(gifski)
library(png)
library(dplyr)
library(patchwork)
library(ggthemes)
library(distill)
library(knitr)
library(rmarkdown)


```

The graph below demonstrates each state's daily new case count over the past few months. Each line represents a different state, and you can hover your mouse over each line to see the state it represents. Note how the cases have been steadily decreasing over time, particularly after the second surge of cases during April. The trend of cases after this surge has massively decreased, far beyond anything before, and far beyond what lockdowns had achieved.

```{r}
new_cases_plot_interactive <- read_rds("new_cases_state_plot.rds")
new_cases_plot_interactive
```

Vaccinations began in earnest during the months of April to May, only a few weeks before the large reduction in cases seen above. This lines up with the [full protection of a vaccination](https://wexnermedical.osu.edu/blog/how-long-for-covid-vaccine-to-work) being achieved two weeks after the first or second dose. However, the rate of vaccination has dropped significantly despite the fact that [less than half of the US population has been vaccinated](https://ourworldindata.org/covid-vaccinations?country=USA). This lack of vaccination could result in [Covid-19 becoming endemic](https://www.nature.com/articles/d41586-021-00396-2), meaning it would be regularly found among people, just like the flu. 

```{r}
vacc_state_interactive <- read_rds("vacc_state.rds")
vacc_state_interactive
```
```{r}
anim_graph <- read_rds("anim_plot.rds")
anim_graph
```

test